Process-based phenotypes: an application to the ontology of cell physiology

### 2011-11-28 paper/drinking.tex

\subsection{Pre- vs. post-composed ontology}
We implemented the CPO using only a few patterns for formulating
phenotypes involving processes.

\subsection{Future work}
Formal, axiomatic system for process qualities, maybe based on PSL,
FOIS paper 2010

one example:...

\subsection{Conclusion}

>>>>

\subsection{Pre- vs. post-composed ontology}
We implemented the CPO using a pattern-based approach to formulating
phenotypes involving processes. The patterns we identify use
pre-existing ontologies, in particular the PATO ontology and the
classification of cellular processes as well as cellular components in
the GO. The result is a large ontology in which classes for phenotypes
are {\em pre-composed}: they are named and defined within an OWL
ontology. However, the large size of the resulting ontology may impair
its utility for data annotation and integration, and software tools
may not always support such very large ontologies. The alternative to
pre-composing all possible phenotype classes using the patterns we
describe is to dynamically generate appropriately defined classes at
the time at which they are being used. To achieve this goal, software
must be developed to support ontology users in applying these patterns
and generate the appropriate class description when required.

% \subsection{Future work}
% Formal, axiomatic system for process qualities, maybe based on PSL,
% FOIS paper 2010

% one example:...

% \subsection{Conclusion}
